---
title: "Homelessness Midpoint Deliverable"
author: "Gabby, Vincent, and Eric"
date: "11/17/2019"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(leaflet)
library(leaflet.minicharts)
library(knitr)
library(ggplot2)
library(ggpubr)
library(stringr)

source("scripts/data_wrangling.R")

source("scripts/shelter.R")
source("scripts/cost_of_living.R")
source("scripts/sum_info.R")
source("scripts/sum_table.R")

states <- read.csv("data/homelessness/states.csv", stringsAsFactors = FALSE)
state_populations <- read.csv("data/homelessness/Population-by-state.csv", stringsAsFactors = FALSE)
homelessness <- read.csv("data/homelessness/2007-2016-Homelessnewss-USA.csv", stringsAsFactors = FALSE)

cpi_2016 <- read.csv("data/cost-of-living/cost-of-living-2016.csv",
                    stringsAsFactors = FALSE)

homeless_population_analysis <- homelessPopulationAnalysis(states, state_populations, homelessness) 
```

## Topic
Our domain of interest is Homelessness. In the Seattle King County area, there are about 12,500 homeless people living on the streets or in shelters. This not only makes the living environment of Seattle worse but also impacts the citizens’ daily life(crime, policing, junk/RVs, harassment etc). Confronted with this in our daily lives, we are interested in better understanding the issue locally and nationally including some of the factors contributing to it.

## Summary
```{r summary, include=FALSE}
summary <- get_summary_info(homeless_population_analysis)
```
In 2016 there were `r summary$total_homeless` in the US, with an average of `r summary$avg_homeless` in each State. `r summary$state_least_homeless` had the fewest homeless and `r summary$state_most_homeless` the most.  There were a total of `r summary$homeless_vets` homeless veterans, `r summary$homeless_u18` homeless under 18 years old, and `r summary$homeless_family` homeless with families.

## Table 

```{r table, message=FALSE, echo=FALSE, warning=FALSE}
get_sum_table(cpi_2016, homelessness, state_populations)
```

This summary table provides aggregate information of 10 states with the highest percentages of Homeless population. It also comes with the average CPI(Cosumer Price Index), total populaion of each state. We include this table to show you which states are most impacted by Homeless problem.

## Shelter Analysis
The visualization below illustrates the proportion of Sheltered Homeless to Unsheltered Homeless individuals, in each State in 2016. To make variance even more apparent, the pie charts gets larger when there is a high proportion of Unsheltered Homeless.

You can see that states with more moderate climates, such as California and Florida have greater portions of unsheltered homeless.
```{r homelessness, message=FALSE, echo=FALSE, warning=FALSE}
shelterAnalysis(states, state_populations, homelessness)
```

## CPI Analysis
The following is a preview. As you can see in the scatter plot, there is a potential correaltion between CPI and Homeless rate. However, it is not quite obvious. To visualize the potential correlation between higher cost of living and Homeless rate, we have included another chart for better comparison.  

```{r charts, fig.width=12, fig.height=5, message=FALSE, echo=FALSE, warning=FALSE}
get_charts(cpi_2016, homelessness)
```
  
This bar chart includes 10 representative cities ranging from cities with below average CPIs to those with the higest CPIs. As you can tell, as the CPI goes up, the Homelessness rates goes up. We have calculated the number of Homeless people in 1 Million people to eliminate the influence by city population(larger cities tend to have higher CPIs and higher population, which means more homeless people). Note that Atlanta and Seattle are two outlier in this comparison, with unusual high population of Homeless. However, this can't deny that Homeless rate is correlated with CPI. We should be cocerned that Seattle's high homeless population has something to do with other factors such as lack of governance and bad drug control, etc. 

## Chart 3 Observations 

