---
title: "Index"
author: "Gabby, Vincent, and Eric"
date: "11/17/2019"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(leaflet)
library(leaflet.minicharts)
library(knitr)

source("scripts/shelter.R")
source("scripts/cost_of_living.R")
source("scripts/sum_info.R")
source("scripts/sum_table.R")

states <- read.csv("data/homelessness/states.csv", stringsAsFactors = FALSE)
state_populations <- read.csv("data/homelessness/Population-by-state.csv", stringsAsFactors = FALSE)
homelessness <- read.csv("data/homelessness/2007-2016-Homelessnewss-USA.csv", stringsAsFactors = FALSE)

shelter_summary <- shelterAnalysis(states, state_populations, homelessness)
```

## Introductory paragraph:
Our domain of interest is Homelessness. In the Seattle King County area, there are about 12,500 homeless people living on the streets or in shelters. This not only makes the living environment of Seattle worse but also impacts the citizens’ daily life(crime, policing, junk/RVs, harassment etc). Confronted with this in our daily lives, we are interested in better understanding the issue locally and nationally including some of the factors contributing to it.

## Summary Paragraph
```{r summary, include=FALSE}
homelessness <- read.csv("data/homelessness/2007-2016-Homelessnewss-USA.csv", stringsAsFactors = FALSE)
summary <- get_summary_info(homelessness)
```
The average number of homeless people between 2007 - 2016 was `r summary$avg_unshel_hl`.
Number of homeless veterans in 2016 was `r summary$homeless_vets`.
Which state had the least homeless people in 2016? `r summary$latest_state_most_hl`.
year with most homeless people `r summary$year_most_homeless`
Total homeless people in 2016 `r sum(shelter_summary$totalHomeless)`
National average of percent of homeless people with shelter `r mean(shelter_summary$sheltered)`

## Table 
```{r table, include=FALSE}
kable(sum_table, digits = 2, align = "l",
      col.names = c("State", "Avg.CPI", "Homeless Population",
                    "Total Population", "Percentage(%)"),
      caption = "Summary Table")
```

This summary table provides aggregate information of 10 states with the highest percentages of Homeless population. It also comes with the average CPI(Cosumer Price Index), total populaion of each state. We include this table to show you which states are most impacted by Homeless problem.

## Shelter Analysis
```{r homelessness, include=FALSE}

#map <- leaflet(data = summary, width = "100%", height = "400px") %>%
#  addTiles() %>%
#  setView(lng = -95.7129, lat = 37.0902, zoom = 2) %>% 
#  addMinicharts(
#    summary$longitude, summary$latitude,
#    type = "pie",
#    chartdata = select(summary, shelteredHomeless, unshelteredHomeless),
#    width = 20 / summary$sheltered
#  )

# map
```

## Chart 2 Observations 
```{r cost_vs_homeless, include=FALSE}
scatter_plot 
```
This is a preview. As you can see in the scatter plot, there is a potential correaltion between CPI and Homeless rate. However, it is not quite obvious. To visualize the potential correlation between higher cost of living and Homeless rate, we have included the following chart for better comparison. 
```{r barchart, include=FALSE}
bar_chart
```

This bar chart includes 10 representative cities ranging from cities with below average CPIs to those with the higest CPIs. As you can tell, as the CPI goes up, the Homelessness rates goes up. We have calculated the number of Homeless people in 1 Million people to eliminate the influence by city population(larger cities tend to have higher CPIs and higher population, which means more homeless people). Note that Atlanta and Seattle are two outlier in this comparison, with unusual high population of Homeless. However, this can't deny that Homeless rate is correlated with CPI. We should be cocerned that Seattle's high homeless population has something to do with other factors such as lack of governance and bad drug control, etc. 

## Chart 3 Observations 

